Tracing the Hercules stream around the Galaxy

### 2010-09-11 tex/hercules.tex
groups-simulations: add vlos uncertainty figure

\clearpage
\begin{figure}
\includegraphics[width=0.5\textwidth]{distuncertain.ps}
\includegraphics[width=0.5\textwidth]{df.ps}\\
\includegraphics[width=0.5\textwidth]{slope.ps}
\includegraphics[width=0.5\textwidth]{barstrength.ps}
\caption{Variation of the predicted velocity distribution at R = 1.075
  \Ro , $\phi = -21^{\circ}$ (d= 0.4 \Ro, $l$ = 270$^{\circ}$) with
  distance uncertainties; parameters and shape of the distribution
  function; shape of the rotation curve; and bar
  strength.}\label{fig:1dvar}
\end{figure}

>>>>

\clearpage
\begin{figure}
\includegraphics[width=0.35\textwidth]{distuncertain.ps}
\includegraphics[width=0.35\textwidth]{vlosuncertain.ps}\\
\includegraphics[width=0.35\textwidth]{df.ps}
\includegraphics[width=0.35\textwidth]{slope.ps}\\
\includegraphics[width=0.35\textwidth]{barstrength.ps}
\caption{Variation of the predicted velocity distribution at R = 1.075
  \Ro , $\phi = -21^{\circ}$ (d= 0.4 \Ro, $l$ = 270$^{\circ}$) with
  distance uncertainties; line-of-sight velocity uncertainties;
  parameters and shape of the distribution function; shape of the
  rotation curve; and bar strength.}\label{fig:1dvar}
\end{figure}
